Query Optimization for Dynamic Imputation

### 2017-05-15 paper/experiments.tex
paper: squeeze

There are 6 tables in the NHANES data set. We use three tables for our experiments:

\begin{itemize}
	\item \texttt{demo}: demographic information of subjects
	\item \texttt{exams}: physical exam results
	\item \texttt{labs}: laboratory exam results
\end{itemize}

@@

\Cref{fig:runtimes} summarizes the performance results. The quality-optimized
queries are an order-of-magnitude faster than the baseline. We get another order-of-magnitude speedup when optimizing for performance. This performance
differential means it is feasible
to explore multiple imputation operations (including more expensive operators) when using
\ProjectName{}, in contrast to the traditional approach of fully imputing the dataset.

>>>>

There are 6 tables in the NHANES data set. We use three tables for our experiments: demographic information of subjects (\texttt{demo}), physical exam results (\texttt{exams}), and laboratory exam results (\texttt{labs}).

@@

\Cref{fig:runtimes} summarizes the performance results. The quality-optimized
queries are an order-of-magnitude faster than the baseline. We get another order-of-magnitude speedup when optimizing for performance.

### 2017-05-15 paper/main.tex
Add max planning time result
paper: minor changes
paper: squeeze

\documentclass[preprint]{vldb}
\usepackage{balance}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[activate={true,nocompatibility},final,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
\usepackage[subtle]{savetrees}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[style=numeric,firstinits=true,maxcitenames=2]{biblatex}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{graphicx} % includegraphics
\usepackage{listings} % code samples with syntax hl
\usepackage{stmaryrd}
\usepackage{qtree} % for simple tree diagrams
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{xspace}
\usepackage[all]{nowidow}
\usepackage{enumitem}
\usepackage{hyperref} % load after other packages
\usepackage{cleveref}

@@

\newcommand{\planninglowtime}{0.7}
\newcommand{\planninglowtimepct}{0}
\newcommand{\planninghightime}{2.8}
\newcommand{\planninghightimepct}{14}

\newcommand{\planningmaxtime}{\todo{XXX}} % {34} % TODO

@@

\bibstyle{abbrv}
\balance
\printbibliography

>>>>

\documentclass[preprint]{vldb}
\usepackage{balance}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[activate={true,nocompatibility},final,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
\usepackage[subtle]{savetrees}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[style=savetrees,firstinits=true,maxcitenames=2]{biblatex}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{graphicx} % includegraphics
\usepackage{listings} % code samples with syntax hl
\usepackage{stmaryrd}
\usepackage{qtree} % for simple tree diagrams
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{xspace}
\usepackage[all]{nowidow}
\usepackage{enumitem}
\usepackage{hyperref} % load after other packages
\usepackage{cleveref}

@@

\newcommand{\planningtimelow}{0.7 ms}
\newcommand{\planningtimelowpct}{0}
\newcommand{\planningtimehigh}{2.8 ms}
\newcommand{\planningtimehighpct}{14}

\newcommand{\planningtimemax}{113 ms} % max planning time of any single query
\newcommand{\planningtimepninetynine}{4 ms} % 99 percentile planning time of any single query
\newcommand{\planningtimepninetyninepointnine}{14 ms} % 99.9 percentile planning time of any single query

@@

\bibstyle{abbrv}
\printbibliography
\balance
